Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-30 manuscript_results.Rmd
update

```{r}
library("tidyr")
library("MMWRweek")
library("data.table")
library("caret")
library("purrr")
library("dplyr")
library("tseries")
library("gtools")
library("forecast")
library("scoringutils")
library("covidHubUtils")
library("parallel")
library("future")#https://cran.r-project.org/web/packages/future/vignettes/future-4-issues.html
library("listenv")
library("epitools")
library("ggplot2")
library("sf")
library("forcats")
library("ggplot2")
library("sf")
library("dplyr")
library("scales")  # For `breaks_extended`
library("ggplot2")
library("broom")
library("fields")
library("ggpubr")
library("patchwork")

@@

# Define the date range
end_date <- as.Date(AUTO_AVERAGE_WEEK1_list[[ii]]$target_end_date[i]-7)
start_date <- end_date - 365*2  # 2 years before

@@

i  <- 57
ii <- 8 # state number

@@

# Create a custom color mapping for each variable
custom_colors <- c(
  "AUTO_AR_LB" = colors_ar[1], "ES27_AR_LB" = colors_ar[2], "ES64_AR_LB" = colors_ar[3],
  "AUTO_EPI_LB" = colors_epi[1], "ES27_EPI_LB" = colors_epi[2], "ES64_EPI_LB" = colors_epi[3],
  "AUTO_TMP_LB" = colors_tmp[1], "ES27_TMP_LB" = colors_tmp[2], "ES64_TMP_LB" = colors_tmp[3],
  "AUTO_ADJ_LB" = colors_adj[1], "ES27_ADJ_LB" = colors_adj[2], "ES64_ADJ_LB" = colors_adj[3],
  "AUTO_AVG_LB" = colors_avg[1], "ES27_AVG_LB" = colors_avg[2], "ES64_AVG_LB" = colors_avg[3],

@@

# Save and display the plot
ggsave("Fig4.jpg", combined_plot, width =8, height =5)
print(combined_plot)

>>>>

```{r}
library("tidyr")
library("MMWRweek")
library("data.table")
library("caret")
library("purrr")
library("dplyr")
library("tseries")
library("gtools")
library("forecast")
library("scoringutils")
library("covidHubUtils")
library("parallel")
library("future")#https://cran.r-project.org/web/packages/future/vignettes/future-4-issues.html
library("listenv")
library("epitools")
library("ggplot2")
library("sf")
library("forcats")
library("ggplot2")
library("sf")
library("dplyr")
library("scales")  # For `breaks_extended`
library("ggplot2")
library("broom")
library("fields")
library("ggpubr")
library("patchwork")
library("ggpattern")

@@

# Define the date range
end_date <- as.Date(AUTO_AVERAGE_WEEK1_list[[ii]]$target_end_date[i]-7)
start_date <- end_date - (7*103)  # 2 years before

@@

i  <- 57 # target_end_date
ii <- 8 # state number

@@

custom_colors <- c(
  "AUTO_AR_LB" = colors_ar[1], "ES27_AR_LB" = colors_ar[1], "ES64_AR_LB" = colors_ar[1],
  "AUTO_EPI_LB" = colors_epi[1], "ES27_EPI_LB" = colors_epi[1], "ES64_EPI_LB" = colors_epi[1],
  "AUTO_TMP_LB" = colors_tmp[1], "ES27_TMP_LB" = colors_tmp[1], "ES64_TMP_LB" = colors_tmp[1],
  "AUTO_ADJ_LB" = colors_adj[1], "ES27_ADJ_LB" = colors_adj[1], "ES64_ADJ_LB" = colors_adj[1],
  "AUTO_AVG_LB" = colors_avg[1], "ES27_AVG_LB" = colors_avg[1], "ES64_AVG_LB" = colors_avg[1],

  "AUTO_AR" = colors_ar[1], "ES27_AR" = colors_ar[1], "ES64_AR" = colors_ar[1],
  "AUTO_EPI" = colors_epi[1], "ES27_EPI" = colors_epi[1], "ES64_EPI" = colors_epi[1],
  "AUTO_TMP" = colors_tmp[1], "ES27_TMP" = colors_tmp[1], "ES64_TMP" = colors_tmp[1],
  "AUTO_ADJ" = colors_adj[1], "ES27_ADJ" = colors_adj[1], "ES64_ADJ" = colors_adj[1],
  "AUTO_AVG" = colors_avg[1], "ES27_AVG" = colors_avg[1], "ES64_AVG" = colors_avg[1]
)

# define a manual pattern scale
custom_patterns <- c(
  # AR
  "AUTO_AR"      = "circle",      "AUTO_AR_LB"      = "circle",
  "ES27_AR"      = "stripe",      "ES27_AR_LB"      = "stripe",
  "ES64_AR"      = "crosshatch",  "ES64_AR_LB"      = "crosshatch",
  # EPI
  "AUTO_EPI"     = "circle",      "AUTO_EPI_LB"     = "circle",
  "ES27_EPI"     = "stripe",      "ES27_EPI_LB"     = "stripe",
  "ES64_EPI"     = "crosshatch",  "ES64_EPI_LB"     = "crosshatch",
  # TMP
  "AUTO_TMP"     = "circle",      "AUTO_TMP_LB"     = "circle",
  "ES27_TMP"     = "stripe",      "ES27_TMP_LB"     = "stripe",
  "ES64_TMP"     = "crosshatch",  "ES64_TMP_LB"     = "crosshatch",
  # ADJ
  "AUTO_ADJ"     = "circle",      "AUTO_ADJ_LB"     = "circle",
  "ES27_ADJ"     = "stripe",      "ES27_ADJ_LB"     = "stripe",
  "ES64_ADJ"     = "crosshatch",  "ES64_ADJ_LB"     = "crosshatch",
  # AVG
  "AUTO_AVG"     = "circle",      "AUTO_AVG_LB"     = "circle",
  "ES27_AVG"     = "stripe",      "ES27_AVG_LB"     = "stripe",
  "ES64_AVG"     = "crosshatch",  "ES64_AVG_LB"     = "crosshatch"
)

#custom_patterns <- custom_patterns[custom_patterns != "circle"]

plot1 <- ggplot(W1, aes(x = Best_Result,
                        pattern = Best_Result,
                        fill    = Best_Result)) +
  geom_bar_pattern(
    colour        = NA,            # no border
    pattern_fill  = "black",
    pattern_size  = 0.2,
    pattern_angle = 45             # set globally, not inside aes()
  ) +
  scale_fill_manual(values   = custom_colors) +
  scale_pattern_manual(values = custom_patterns) +
  labs(title = "Best model on the 48 U.S. states (W1)",
       x = NULL, y = "Number of states") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ Model_Type, scales = "free_x") +
  guides(pattern_angle = "none")  # this line is optional now but safe

plot2 <- ggplot(W2, aes(x = Best_Result,
                        pattern = Best_Result,
                        fill    = Best_Result)) +
  geom_bar_pattern(
    colour        = NA,            # no border
    pattern_fill  = "black",
    pattern_size  = 0.2,
    pattern_angle = 45             # set globally, not inside aes()
  ) +
  scale_fill_manual(values   = custom_colors) +
  scale_pattern_manual(values = custom_patterns) +
  labs(title = "Best model on the 48 U.S. states (W2)",
       x = NULL, y = "Number of states") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ Model_Type, scales = "free_x") +
  guides(pattern_angle = "none")  # this line is optional now but safe

plot3 <- ggplot(W3, aes(x = Best_Result,
                        pattern = Best_Result,
                        fill    = Best_Result)) +
  geom_bar_pattern(
    colour        = NA,            # no border
    pattern_fill  = "black",
    pattern_size  = 0.2,
    pattern_angle = 45             # set globally, not inside aes()
  ) +
  scale_fill_manual(values   = custom_colors) +
  scale_pattern_manual(values = custom_patterns) +
  labs(title = "Best model on the 48 U.S. states (W3)",
       x = NULL, y = "Number of states") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ Model_Type, scales = "free_x") +
  guides(pattern_angle = "none")  # this line is optional now but safe

plot3

plot4 <- ggplot(W4, aes(x = Best_Result,
                        pattern = Best_Result,
                        fill    = Best_Result)) +
  geom_bar_pattern(
    colour        = NA,            # no border
    pattern_fill  = "black",
    pattern_size  = 0.2,
    pattern_angle = 45             # set globally, not inside aes()
  ) +
  scale_fill_manual(values   = custom_colors) +
  scale_pattern_manual(values = custom_patterns) +
  labs(title = "Best model on the 48 U.S. states (W4)",
       x = NULL, y = "Number of states") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ Model_Type, scales = "free_x") +
  guides(pattern_angle = "none")  # this line is optional now but safe

plot4

library(ggpattern)
library(ggplot2)
library(dplyr)

# Assign week labels
W1$Week_Ahead <- "W1"
W2$Week_Ahead <- "W2"
W3$Week_Ahead <- "W3"
W4$Week_Ahead <- "W4"

# Combine all weeks
all_weeks <- bind_rows(W1, W2, W3, W4)

# Create the patterned plot
combined_plot <- ggplot(all_weeks, aes(x = Best_Result, 
                                       fill = Best_Result,
                                       pattern = Best_Result)) +
  geom_bar_pattern(
    pattern_fill  = "black",
    pattern_size  = 0.1,
    pattern_angle = 45,  # set globally
    colour        = NA
  ) +
  scale_fill_manual(values = custom_colors) +
  scale_pattern_manual(values = custom_patterns) +  # define this before
  labs(title = "Best model based on the lowest mean WIS",
       subtitle = "Results for the 48 states on the contiguous U.S. by target week",
       x = "", y = "Number of states",
       fill = "Best model",
       pattern = "Best model") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold"),legend.position = "none") +
  facet_grid(Week_Ahead ~ Model_Type, scales = "free_x") +
  guides(pattern_angle = "none")  # just in case

# Save and display the plot
ggsave("Fig4.jpg", combined_plot, width = 7, height = 6)
print(combined_plot)
```

```{r}
# Create a custom color mapping for each variable
custom_colors <- c(
  "AUTO_AR_LB" = colors_ar[1], "ES27_AR_LB" = colors_ar[2], "ES64_AR_LB" = colors_ar[3],
  "AUTO_EPI_LB" = colors_epi[1], "ES27_EPI_LB" = colors_epi[2], "ES64_EPI_LB" = colors_epi[3],
  "AUTO_TMP_LB" = colors_tmp[1], "ES27_TMP_LB" = colors_tmp[2], "ES64_TMP_LB" = colors_tmp[3],
  "AUTO_ADJ_LB" = colors_adj[1], "ES27_ADJ_LB" = colors_adj[2], "ES64_ADJ_LB" = colors_adj[3],
  "AUTO_AVG_LB" = colors_avg[1], "ES27_AVG_LB" = colors_avg[2], "ES64_AVG_LB" = colors_avg[3],

@@

# Save and display the plot
#ggsave("Fig4.jpg", combined_plot, width =8, height =5)
print(combined_plot)
